The \dealii{} Library, Version 9.4

### 2022-04-23 9.4/paper.tex
Draft

@@

\author[6]{Timo~Heister}
 \affil[6]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister/jiaqi2@clemson.edu}}}

@@

 \author[9,10]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch/proell@lnm.mw.tum.de}}}
 \affil[10]{Department of Information Technology,
   Uppsala University,
   Box 337, 751\,05 Uppsala, Sweden.
   {\texttt{martin.kronbichler@it.uu.se}}}

@@

\begin{abstract}
  This paper provides an overview of the new features of the finite element
  library \dealii, version 9.3.
\end{abstract}

@@

The major changes of this release are:
%
\begin{itemize}
  \item TODO;
  \item TODO new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%
In addition, we discuss the \candi{} installation program in Section~\ref{subsec:candi}.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item TODO.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Topic 1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Topic 2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Topic 3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Topic 4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Topic 5}

@@

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{TODO} TODO.

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
\item ``\texttt{TODO}'' TODO.
\end{itemize}

@@

The 9.4 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_3_0_and_9_4_0.html}
{around TODO incompatible changes}; see \cite{changes94}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item TODO
  \item TODO

@@

The original \dealii{} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}, and a more recent
publication documenting \dealii{}'s design decisions is available as \cite{dealII2020design}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
    \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
    \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
    \item For $hp$-adaptivity: \cite{BangerthKayserHerold2007};
    \item For partition-of-unity (PUM) and finite element enrichment methods:
           \cite{Davydov2016};
    \item For matrix-free and fast assembly techniques:
          \cite{KronbichlerKormann2012,KronbichlerKormann2019};
    \item For computations on lower-dimensional manifolds:
          \cite{DeSimoneHeltaiManigrasso2009};
    \item For curved geometry representations and manifolds:
          \cite{HeltaiBangerthKronbichlerMola2019};
    \item For integration with CAD files and tools:
          \cite{HeltaiMola2015};
    \item For boundary element computations:
          \cite{GiulianiMolaHeltai-2018-a};
    \item For the \texttt{LinearOperator} and
      \texttt{Packaged\-Operation} facilities:
          \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
    \item For uses of the \texttt{WorkStream} interface:
          \cite{TKB16};
    \item For uses of the \texttt{ParameterAcceptor} concept, the
          \texttt{MeshWorker::ScratchData} base class, and the
          \texttt{ParsedConvergenceTable} class:
          \cite{SartoriGiulianiBardelloni-2018-a};
    \item For uses of the particle functionality in \dealii{}:
          \cite{GLHPB18}.
          \vfill\null
  \end{itemize}
\end{multicols}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
TODO.

>>>>

\graphicspath{{svg/}}

@@

\author[6]{Timo~Heister}
 \affil[6]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister@clemson.edu}}}

@@

 \author[9,10]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch@lnm.mw.tum.de}}}
 \affil[10]{Department of Information Technology,
   Uppsala University,
   Box 337, 751\,05 Uppsala, Sweden.
   {\texttt{martin.kronbichler@it.uu.se}}}

@@

\begin{abstract}
  This paper provides an overview of the new features of the finite element
  library \dealii, version 9.4.
\end{abstract}

@@

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Performance improvement of particle infrastructure (see Section~\ref{sec:particles});
  \item Two new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item \texttt{DataOutResample} does not output a numerical solution 
  on the cells of the original triangulation but interpolates the result 
  onto a second triangulation (that can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free, leverages the functionality of p4est (>v.2.2),
  and its algorithm is described in \cite{burstedde2020parallel}. Based on the obtained information,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this feature could be used in the future to allow
  particle simulations, where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
\end{itemize}
%
The changelog lists more than 150 other features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances in simplex- and mixed-mesh support}\label{sec:simplex}

We continued to work on the simplex- and mixed-mesh support. We fixed
many bugs and generalized existing functions that only worked for
hypercube shaped cells. Most notable new functions are:

\begin{figure}[!t]

  \centering

  \begin{tikzpicture}[scale=1.7]

    \coordinate (0) at (0,0);
    \coordinate (1) at (1,0);
    \coordinate (2) at (0,1);

    \coordinate (3) at (0,0.5);
    \coordinate (4) at (0.5,0.5);
    \coordinate (5) at (0.5,0);

    \foreach \i in {0,1, 2, 3, 4, 5}
    \draw[blue,fill=blue] (\i) circle (1.1pt) node [below] {};

    \draw (0) --(1) -- (2) -- (0);
    \draw (3) --(4) -- (5) -- (3);

  \end{tikzpicture}
  \qquad\qquad
  \begin{tikzpicture}[scale=1.3]

    \coordinate (0) at (0,0,0);
    \coordinate (1) at (0,0,1);
    \coordinate (2) at (1,0,0);
    \coordinate (3) at (0,1,0);
    \coordinate (4) at (0,0,0.5);
    \coordinate (6) at (0.5,0,0);
    \coordinate (7) at (0,0.5,0);
    \coordinate (5) at (0.5,0.0,0.5);
    \coordinate (8) at (0.0,0.5,0.5);
    \coordinate (9) at (0.5,0.5,0.0);

    \draw (0) -- (1) -- (2) -- (0);
    \draw (0) -- (1) -- (3) -- (0);
    \draw (1) -- (2) -- (3) -- (1);

    \draw[-, fill=red!30, opacity=.5] (4)--(6)--(7)--cycle;
    \draw[-, fill=red!30, opacity=.5] (0)--(6)--(7)--cycle;
    \draw[-, fill=red!30, opacity=.5] (0)--(4)--(7)--cycle;
    \draw[-, fill=red!30, opacity=.5] (0)--(4)--(6)--cycle;

    \draw[-, fill=blue!30, opacity=.5] (1)--(4)--(5)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (1)--(4)--(8)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (4)--(5)--(8)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (1)--(5)--(8)--cycle;

    \draw[-, fill=green!30, opacity=.5] (2)--(5)--(6)--cycle;
    \draw[-, fill=green!30, opacity=.5] (2)--(6)--(9)--cycle;
    \draw[-, fill=green!30, opacity=.5] (2)--(5)--(9)--cycle;
    \draw[-, fill=green!30, opacity=.5] (5)--(6)--(9)--cycle;

    \draw[-, fill=orange!30, opacity=.5] (7)--(8)--(9)--cycle;
    \draw[-, fill=orange!30, opacity=.5] (3)--(7)--(9)--cycle;
    \draw[-, fill=orange!30, opacity=.5] (3)--(7)--(8)--cycle;
    \draw[-, fill=orange!30, opacity=.5] (3)--(8)--(9)--cycle;

    \foreach \i in {0,1,2,3,4,5,6,7,8,9}
    \draw[blue,fill=blue] (\i) circle (1.0pt) node [below] {};

  \end{tikzpicture}
  \begin{tikzpicture}[scale=1.3]

    \coordinate (0) at (0,0,0);
    \coordinate (1) at (0,0,1);
    \coordinate (2) at (1,0,0);
    \coordinate (3) at (0,1,0);
    \coordinate (4) at (0,0,0.5);
    \coordinate (6) at (0.5,0,0);
    \coordinate (7) at (0,0.5,0);
    \coordinate (5) at (0.5,0.0,0.5);
    \coordinate (8) at (0.0,0.5,0.5);
    \coordinate (9) at (0.5,0.5,0.0);

    \draw (0) -- (1) -- (2) -- (0);
    \draw (0) -- (1) -- (3) -- (0);
    \draw (1) -- (2) -- (3) -- (1);

    \draw[-, fill=red!30, opacity=.5] (4)--(5)--(6)--cycle;
    \draw[-, fill=red!30, opacity=.5] (4)--(5)--(8)--cycle;
    \draw[-, fill=red!30, opacity=.5] (4)--(6)--(8)--cycle;
    \draw[-, fill=red!30, opacity=.5] (5)--(6)--(8)--cycle;

%    \draw[-, fill=blue!30, opacity=.5] (4)--(6)--(7)--cycle;
%    \draw[-, fill=blue!30, opacity=.5] (4)--(6)--(8)--cycle;
%    \draw[-, fill=blue!30, opacity=.5] (4)--(7)--(8)--cycle;
%    \draw[-, fill=blue!30, opacity=.5] (6)--(7)--(8)--cycle;

%    \draw[-, fill=green!30, opacity=.5] (6)--(7)--(8)--cycle;
%    \draw[-, fill=green!30, opacity=.5] (6)--(7)--(9)--cycle;
%    \draw[-, fill=green!30, opacity=.5] (6)--(8)--(9)--cycle;
%    \draw[-, fill=green!30, opacity=.5] (7)--(8)--(9)--cycle; 
%        
    \draw[-, fill=blue!30, opacity=.5] (5)--(6)--(8)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (5)--(6)--(9)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (5)--(8)--(9)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (6)--(8)--(9)--cycle;

    \foreach \i in {0,1,2,3,4,5,6,7,8,9}
    \draw[blue,fill=blue] (\i) circle (1.0pt) node [below] {};

  \end{tikzpicture}
  \begin{tikzpicture}[scale=1.3]

    \coordinate (0) at (0,0,0);
    \coordinate (1) at (0,0,1);
    \coordinate (2) at (1,0,0);
    \coordinate (3) at (0,1,0);
    \coordinate (4) at (0,0,0.5);
    \coordinate (6) at (0.5,0,0);
    \coordinate (7) at (0,0.5,0);
    \coordinate (5) at (0.5,0.0,0.5);
    \coordinate (8) at (0.0,0.5,0.5);
    \coordinate (9) at (0.5,0.5,0.0);

    \draw (0) -- (1) -- (2) -- (0);
    \draw (0) -- (1) -- (3) -- (0);
    \draw (1) -- (2) -- (3) -- (1);

%    \draw[-, fill=red!30, opacity=.5] (4)--(5)--(6)--cycle;
%    \draw[-, fill=red!30, opacity=.5] (4)--(5)--(8)--cycle;
%    \draw[-, fill=red!30, opacity=.5] (4)--(6)--(8)--cycle;
%    \draw[-, fill=red!30, opacity=.5] (5)--(6)--(8)--cycle;

    \draw[-, fill=red!30, opacity=.5] (4)--(6)--(7)--cycle;
    \draw[-, fill=red!30, opacity=.5] (4)--(6)--(8)--cycle;
    \draw[-, fill=red!30, opacity=.5] (4)--(7)--(8)--cycle;
    \draw[-, fill=red!30, opacity=.5] (6)--(7)--(8)--cycle;

    \draw[-, fill=blue!30, opacity=.5] (6)--(7)--(8)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (6)--(7)--(9)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (6)--(8)--(9)--cycle;
    \draw[-, fill=blue!30, opacity=.5] (7)--(8)--(9)--cycle;

%    \draw[-, fill=orange!30, opacity=.5] (5)--(6)--(8)--cycle;
%    \draw[-, fill=orange!30, opacity=.5] (5)--(6)--(9)--cycle;
%    \draw[-, fill=orange!30, opacity=.5] (5)--(8)--(9)--cycle;
%    \draw[-, fill=orange!30, opacity=.5] (6)--(8)--(9)--cycle;

    \foreach \i in {0,1,2,3,4,5,6,7,8,9}
    \draw[blue,fill=blue] (\i) circle (1.0pt) node [below] {};

  \end{tikzpicture}

  \caption{New refinement strategies for triangles and tetrahedrons: triangles
  are subdivided in 4 children and tetrahedrons 8 ones.}\label{fig:refinement}

\end{figure}

\begin{itemize}
\item Experimental support of locally refined meshes. FEM on locally refined
meshes requires 1) the possibility to locally refine the mesh (see Figure~\ref{fig:refinement})
and 2) appropriate hanging-node constraints. For 3D, we are in progress to
implement the missing constraint definitions.
\item TODO
\end{itemize}

Furthermore, we continued to remove the usage of  \texttt{GeometryInfo} from
the library and to replace the instances by more general equivalent functions, which
in many cases rely of \texttt{ReferenceCell}. Once all instance of 
\texttt{GeometryInfo} are remove, we will deprecate the class.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Repartitioning of distributed meshes}\label{sec:repartitioning}

Until now, distributed meshes were either partitioned statically (\texttt{parallel::\allowbreak fullydistributed::\allowbreak Triangulation}; short \texttt{p::f::T}) or used a
fixed policy to partition the cells among processes
(\texttt{parallel::\allowbreak distributed::\allowbreak Triangulation}; short \texttt{p::d::T}). For latter, we
use a Morton-order as the backend of that class---\texttt{p4est}---does. Fixed Morton-order
might provide very good performance in terms in communication and
setup costs, but might be non-optimal when interfacing with other
libraries that have fixed partitioning, most notably a Cartesian
partitioning, themselves.

New utility functions from the \texttt{RepartitioningPolicyTools} can be
used now to create a new \texttt{p::f::T} instances,
given a distributed triangulation (\texttt{p::f::T} or \texttt{p::d::T}) and a vector with the new owners of locally
owned cells. The workflow is shown in the following listing:
\begin{c++}
// original triangulation
parallel::distributed::Triangulation<dim> tria(comm);

// select a partitioning policy and use it
const RepartitioningPolicyTools::Cartesian<dim> policy(tria);
const auto construction_data = TriangulationDescription::Utilities::
  create_description_from_triangulation(tria, policy.partition(tria));

// create the new triangulation
parallel::fullydistributed::Triangulation<dim> tria_pft(comm);
tria_pft.create_triangulation(construction_data);
\end{c++}
Instead of using one of the predefined partitioning policies, users
can write their own by implementing the \texttt{RepartitioningPolicyTools::Base} interface. Similarly to the
active level, also the multigrid levels can be repartitioned arbitrarily.

\begin{figure}
    \centering
    \def\svgwidth{0.8\columnwidth}
    \input{svg/repartitioning.pdf_tex}
    \caption{Visualization of the repartitioning process: after 
    cells are assigned new ranks, each process collect sends the cells incl. 
    ghost cells to the new owner. There incoming cells are processed, duplicates
    are removed and the local part of the triangulation is built.}\label{fig:repartitioning}
\end{figure}

The setup process is visualized in Figure~\ref{fig:repartitioning}. First cells, incl. their
surrounding (ghost) cells and their parent cells, are collected and 
sent to the new owner. On the
receiving side, the set of all cells are combined and possible duplicates
are removed. This information is enough to construct a new triangulation.
For sending/receiving, we apply consensus-based algorithms~\cite{hoefler2010scalable}, which
we introduced in the library in release 9.2~\cite{dealII92}. Consensus-based 
algorithms are used also in \cite{ibanez2016pumi} for repartitioning.

In future releases, we plan to add support for repartitioning based on distributed graph
partitioning libraries, e.g., \texttt{ParMETIS} of \texttt{Zotan}. Furthermore, we intend to extend the 
\texttt{p::f::T} with adaptivity support.
With this and and the new repartitionging features, \texttt{p::f::T}
could be selfconsistent like \texttt{p::d::T}, which is an important
step towards the support of AMR also for distributed simplex and mixed meshes
(see also Subsection~\ref{sec:simplex}).

%We would like to note that we provide a similar class also for repartitioning
%of vectors: \texttt{Noncontiguous\allowbreak Partitioner} from the
%\texttt{Utilities::MPI} namespace.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances in matrix-free infrastructure}\label{sec:mf}

In the matrix-free infrastructure, we have added many new features. Most
notably:
\begin{itemize}
\item Improved support of Hessians: just like values and gradients can be
evaluated and integrated during matrix-free loops, one can do this now
also for Hessians both for cells and faces. This enables, e.g., to write
a matrix-free version of step-47, which solves the biharmonic equation with DG.
\item Cell-centric loops now also allow to access to gradients and Hessians
of neighboring cells on faces. The major obstacle here was to reorientation
of theses in the case of arbitrary orientated cells on unstructured meshes.
\item Users can now create their own cell batches, by providing \texttt{FEEvaluation::reinit()} a list of cell IDs. \texttt{FEEvaluation}
accesses the appropriate data and reshuffles mapping data accordingly on
the fly to enable vectorization over cells. The new feature is useful in many
contexts. Examples are application with sharp interfaces (e.g., two phase flow
or shock capturing) where one needs to treat cells that are ``cut'' by
the interface in a special way. A challenge is that cell batchs
might contain cut or not-cut cell, making vectorization potentially more complication. One way to deal with such cell batches it to apply masks if
the code paths do not diverge too much
(many functions of \texttt{FEEvaluation} allows this). Another way is to
categorize cells during \texttt{MatrixFree::reinit()} in such a way that mixed cell batches do not occur. However, calling  \texttt{MatrixFree::reinit()}
might be too expensive if a very dynamic system is given, which requires
recatorization in each time step. Doing this on-the-fly might be a cheep alternative, even if not computationally optimal during matrix-free loops.
\end{itemize}
Besides these new features, we improved the performance of 
hanging-node-constraint evaluation on the CPU. Instead of performing
quasi-dense matrix-vector multiplications~\cite{KronbichlerKormann2012}, we now use an
approach based on inplace interpolation and sumfactorization, similarly
as we already did in the GPU code~\cite{ljungkvist2017matrix}. The algorithm is described
in \cite{munch2022hn} and performance numbers are shown, indicating a reduction
of overhead of cells with hanging nodes by a factor of 10$\times$.

Furthermore, we have performed a major restructuring of internals
of the \texttt{FEEvaluation} classes. This will enable us to add more
simply the support of new element types in the future, e.g., of 
Raviart--Thomas and Nedelec elements.

%\begin{c++}
%additional_data.mapping_update_flags = ... | update_hessians;
%\end{c++}
%
%\begin{c++}
%FEEvaluation<dim> phi(matrix_free);
%
%phi.reinit(cell);
%phi.gather_evaluate(src, ... | EvaluationFlags::hessians);
%
%for(const auto q : phi.quadrature_point_indices())
%  phi.submit_hessian(phi.get_hessian(q), q);
%  
%phi.integrate_scatter(... | EvaluationFlags::hessians, dst);
%\end{c++}
%
%... similar for faces; can be used to implement biharmonic equation (like in
%step-X)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances in multigrid infrastructure}\label{sec:multigrid}

In release 9.3~\cite{dealII93}, we added support for global coarsening multigrid in 
addition to the established local smoothing infrastructure. Global 
coarsening smoothens on the whole computational domain on each
multigrid level, which are obtained by coarsening the finest mesh globally.
For this purpose, we use a sequence of triangulations, on which we perform
the smoothing only on the active levels. To create the sequence of 
triangulations, one can use the functions \texttt{create\_geometric\_coarsening\_sequence()} from the
\texttt{MGTransferGlobalCoarseningTools} namespace. A new version takes an 
instance of \texttt{RepartitioningPolicyTools::Base} (see Subsection~\ref{sec:repartitioning}, which allow to specify the parallel 
distribution of each multigrid level (in contrast to the fixed---first-child---policy in the case of local smoothing). Furthermore, we added support of block vectors,
fixed a number of limitations, and performed performance optimizations of 
the transfer operator; particularly, the redundant copy from/to temporary vectors
has been eliminated and the application of hanging-node constraints are applied
efficiently the same way as in the matrix-free loops (see Subsection~\ref{sec:mf}).

In \cite{munch2022gc}, the performance of \texttt{deal.II}'s local-smoothing and global-coarsening
infrastructure was compared for locally refined meshes. The results indicate that
the local definition of multirgrid levels might introduce load imbalances
in the case of local smoothing so that global coarsening is favorable despite
of potentially more expensive inter-grid transfers. To judge the benefit
of one approach against the other, \texttt{deal.II} provides new functions
\texttt{workload\_imbalance()} and \texttt{vertical\_communication\_efficiency()} 
in the \texttt{MGTools} namespace to estimate the workload imbalance and the
vertical communication efficiency purely based on the given mesh. The publication also points out that not
all types of smoothers are applicable for global coarsening, due to the
presence of hanging-nodes, which is a motivation to add new smoother types
to \dealii.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CutFEM support}\label{sec:cut}

\begin{itemize}
\item new classes
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance improvement of particle infrastructure}\label{sec:particles}

\begin{itemize}
\item describe the new data structure
\item do we have performance numbers?
\end{itemize}

@@

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-82} was contributed by Andrea Bonito (Texas A\&M University) and Diane Guignard (University of Ottawa). It shows how
\dealii{} can be used to implement the
local discontinuous Galerkin (LDG) method for approximating the solution to the bi-Laplacian problem.
\item \texttt{step-85} was contributed by Simon Sticko (Uppsala University). It shows how to use the new CutFEM infrastructure to solve a Poisson 
problem on a circular domain that is embedded in a Cartesian background mesh.
\end{itemize}

%There is also a new program in the code gallery (a collection of
%user-contributed programs that often solve more complicated problems
%than tutorial programs, and intended as starting points for further
%research rather than as teaching tools):
%\begin{itemize}
%\item ``\texttt{TODO}'' TODO.
%\end{itemize}

@@

The 9.4 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_3_0_and_9_4_0.html}
{around 40 incompatible changes}; see \cite{changes94}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item In continuation of our attempt to merge the classes \texttt{DoFHandler} and \texttt{hp::DoFHandler}, we have removed the
  template parameter \texttt{DoFHandlerType} form many classes and
  functions and replaced it by \texttt{dim}/\texttt{spacedim}. Affected
  classes are, e.g., \texttt{SolutionTransfer} and \texttt{DataOut}. 
  \item \texttt{FE\_RaviartThomasNodal} now uses a different polynomial space to allow
for a simpler use for faces in non-standard orientation. The new polynomials
are anisotropic tensor products of Lagrange polynomials on the points of a
Gauss--Lobatto quadrature formula. This change leads to different entries in
the matrices and constraints, for example, but as the resulting polynomial
space spans the same polynomials, no change in accuracy should be expected.
\item We made different changes to the repartitoning of \texttt{parallel::distributed::Triangulation}. Most notably, we have have
removed the default weight (10,000) for consistency reasons with the rest
of the library.

@@

The original \dealii{} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}, and a more recent
publication documenting \dealii{}'s design decisions is available as \cite{dealII2020design}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
    \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019, munch2022gc};
    \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
    \item For $hp$-adaptivity: \cite{BangerthKayserHerold2007};
    \item For partition-of-unity (PUM) and finite element enrichment methods:
           \cite{Davydov2016};
    \item For matrix-free and fast assembly techniques:
          \cite{KronbichlerKormann2012,KronbichlerKormann2019};
    \item For computations on lower-dimensional manifolds:
          \cite{DeSimoneHeltaiManigrasso2009};
    \item For curved geometry representations and manifolds:
          \cite{HeltaiBangerthKronbichlerMola2019};
    \item For integration with CAD files and tools:
          \cite{HeltaiMola2015};
    \item For boundary element computations:
          \cite{GiulianiMolaHeltai-2018-a};
    \item For the \texttt{LinearOperator} and
      \texttt{Packaged\-Operation} facilities:
          \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
    \item For uses of the \texttt{WorkStream} interface:
          \cite{TKB16};
    \item For uses of the \texttt{ParameterAcceptor} concept, the
          \texttt{MeshWorker::ScratchData} base class, and the
          \texttt{ParsedConvergenceTable} class:
          \cite{SartoriGiulianiBardelloni-2018-a};
    \item For uses of the particle functionality in \dealii{}:
          \cite{GLHPB18}.
          \vfill\null
  \end{itemize}
\end{multicols}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.4: updated 23/04/2022 PM
Pasquale	Africa,
Tyler	Anderson,
Francesco	Andreuzzi,
Mathias	Anselmann,
Maximilian	Bergbauer,
Bruno	Blais,
Till	Budde,
Fabian	Castelli,
Praveen	Chandrashekar,
Cu	Cui,
Ivo	Dravins,
Marco	Feder,
Niklas	Fehn,
Johannes	Friedlein,
Sebastian	Fuchs,
Rene	Gassmoeller,
Nicola	Giuliani,
Alexander	Grayver,
Diane	Guignard,
Jake	Harmon,
Sean	Ingimarson,
Pengfei	Jia,
Sebastian	Kinnewig,
Simon	Konrad,
Katharina	Kormann,
Paras	Kumar,
Wenyu	Lei,
Alberto F.	Martin,
Nils	Much,
Lucas	Myers,
Justin	O'Connor,
Judith	Pauen,
Vachan	Potluri,
Raghunandan	Pratoori,
Sebastian	Proell,
Ce	Qin,
Reza	Rastak,
Jose E.	Roman,
Raphael	Schoof,
Magdalena	Schreter,
Konrad	Simon,
Simon	Sticko,
Bruno	Turcksin,
Kuljit S.	Virk,
Michał	Wichrowski,
Niklas Wik,
Jiaqi	Zhang.
